---
title: "Bioshiny Module Library"
author: "cbenoit"
date: "07/10/2020"
output:
  md_document:
    variant: markdown_github
    number_sections: true
  html_document:
    df_print: paged
---
[]!(images/Icurie.jpg) []!(images/Bioshiny.png)

# Description

This library aims to provide R shiny apps developper of the Institut Curie with different modules witch can be used as bricks to build bigger shiny apps. 

# Installation

  + Download and unzip the source code
  + run the following command : renv::init("path_to_bioshiny_module_library_folder/"). This should install the library dependancies.
  + Finally install the library install.packages("path_to_bioshiny_module_library_folder/", type = "source", repos = NULL)
  
# Call a module

To do so you have to call two functions, one in the server and the second in the UI part. 

## Server Part

In the CallModule function you stipulate the library module that you want to call (tipically called ModuleNameServer), and an id for this specific call. 

```{r, eval=FALSE}
  server <- function(input, output, session) {
    observe({
    PCA <- callModule(module = DrawPCAServer2,id = "PCA1",
                     matrix = counts ,
                      metadata = metadata)
    })
}
```

*NB :* Some of the modules accept arguments of type reactiveValues. Description of the arguments are provided in the ModuleNameServer functions' help sections. This wad different modules can communicates and share data objects.

## UI part

In the UI call the corresponding ModuleNameUI function, with the matching id. 

```{r, eval=FALSE}
ui <- dashboardPage(
  dashboardHeader(title = "PCA Module Test"),
  dashboardSidebar(),
  dashboardBody(
    fluidPage(
    fluidRow(
      DrawPCAUI2("PCA1")
    ))
  )
)
```

# Contact

If you have any question or suggestions please contact [pierre.gestraud@curie.fr](mailto:pierre.gestraud@curie.fr) and  [clement.benoit@curie.fr](mailto:clement.benoit@curie.fr)
